Compositional equivalences based on Open pNets

### 2020-02-19 2016-Weak-FH-Bisim/WeakBisim.tex
Fini Fig 7

\begin{figure}[h]
   \centerline{\includegraphics[width=9cm]{XFIG/SimpleProtImpl-WOA}}
  \caption{Weak Open Automaton of the implementation}
   \label{SimpleProtCounter:ImplOA}
\end{figure}

@@

We can now show some of the weak OTs of Figure \ref{SimpleProtCounter:SpecOA-partial} (the full table is included in Appendix \ref{Appendix:FullExample}) :
\smallskip

>>>>

\begin{figure}[h]
   \centerline{\includegraphics[width=11cm]{XFIG/SimpleProtImpl-WOA}}
  \caption{Weak Open Automaton of the implementation}
   \label{SimpleProtCounter:ImplOA}
\end{figure}

@@

We can now show some of the weak OTs of Figure \ref{SimpleProtCounter:ImplOA} (the full table is included in Appendix \ref{Appendix:FullExample}) :
\smallskip

$ WT_1 = \openrule
{\{\texttt{P}\mapsto \texttt{p-a}\}, [\forall \texttt{m}. \texttt{p-a} \neq \texttt{p-send(m)} ], ()}
{000 \OTWeakarrow {\tau} 000}$

$ WT_{3'} = \openrule
  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
    (\texttt{m1\_msg}\gets \texttt{m}, \texttt{m1\_ec}\gets n)}
  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 210}
  \ \forall n\ge 0$

         $ WT_4 = \openrule
         {\{\}, True, (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}+n)}
         {100 \OTWeakarrow {\tau} 210}
         \ \forall n\ge 0$

$ WT_8 = \openrule
         {\{\}, True, ()}
         {201 \OTWeakarrow {\underline{\texttt{out(r1-msg,r1-ec)}}} 202}
         $
